% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[a4paper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Aleksandr O. Vasilev}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6in, 9in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  \href{http://www.s-vfu.ru/user/user.php?id=732071}{North-Eastern Federal University} \\
  42, Kulakovskogo \\
  677000 Yakutsk, Russia
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & +7-924-1734045 \\
    Email: & \href{mailto:haska87@gmail.com}{\tt haska87@gmail.com}  \\ \\
  \end{tabular}
\end{minipage}

\section*{Personal}

\begin{itemize}
\item Born on April 26, 1987
\item Russian Federation Citizen
\item English: Pre-Intermediate
\end{itemize}

\section*{Computer skills}

\begin{itemize}
\item Programming languages: C/C ++, Python
\item Libraries: MPI (Parallelization), FEniCS (FEM), PETSc, SLEPc (Algebra), VTK (Visualisation)
\item Applications: NETGEN (Mesh generation), GMSH (Mesh generation), Paraview (Visualisation)
\item Operating systems: Ubuntu (Linux), Mac OS, Windows OS
\end{itemize}


\section*{Education}

\begin{itemize}

  \item M.Sc. in applied mathematics, North-Eastern Federal University, 2011.
  
  \item Ph.D. in applied mathematics,  North-Eastern Federal University, 2018. \\ Subject: Numerical modeling of neutron diffusion dynamics in a nuclear reactor.
\end{itemize}

\section*{Employment}

\begin{itemize}
\item Programmer, ITERA LLC, Yakutsk, 2011-2011
\item Specialist Expert, Pension Fund of the Russian Federation, Yakutsk, 2011--2012
\item Associate Researcher, North-Eastern Federal University, Yakutsk, 2012--2014
\item Lead Engineer, North-Eastern Federal University, Yakutsk, 2014--2016
\item Engineer programmer, Nuclear Safety Institute of the RAS, Moscow, 2015--present
\item Senior Researcher, North-Eastern Federal University, Yakutsk, 2017--present
\end{itemize}

\section*{Research interests}

\subsection*{Numerical methods}
\begin{itemize}
\item{Multiphysics problems}
\item{Spectral problems} 
\item{Reduction methods}
\item{Parallel algorithms}
\end{itemize}
\subsection*{Applied modeling}
\begin{itemize}
 \item Neutron diffusion in  a nuclear reactor 
 \item Medicine problems
\end{itemize} 

\section*{Awards}
Scholarship of the President of the Russian Federation 2018

\section*{Publications}

\subsection*{Books}
\begin{enumerate}

 
 \item N.M. Afanasyeva, M.Yu. Antonov, V.S. Borisov, A.V. Grigoriev, A.E. Kolesov, P.A. Popov, I.K. Sirditov, A.O. Vasilev, M.V. Vasilieva, P.E. Zakharov edited by P.N. Vabishchevich.
Computational Technologies. Advanced Topics. Moscow: LENAND, 2017.

\end{enumerate} 

\subsection*{Selected articles}

\begin{enumerate}
\item Avvakumov A. V., Strizhov V. F., Vabishchevich P. N., Vasilev A.O. State change modal method for numerical simulation of dynamic processes in a nuclear reactor // Progress in Nuclear Energy. -- 2018. -- Vol. 108. -- P. 240-261.

\item Vabishchevich P.N., Vasil\' ev A.O. Time step selection for the numerical solution of boundary value problems for parabolic equations // Computational Mathematics and Mathematical Physics. -- 2017. -- Vol. 57. -- P. 843-853.

\item Avvakumov A. V., Strizhov V. F., Vabishchevich P. N., Vasilev A.O. Spectral properties of dynamic processes in a nuclear reactor // Annals of Nuclear Energy. -- 2017.  -- Vol. 99.  -- P. 68-79.

\item Avvakumov A.V., Vabishchevich P.N., Vasil'ev A.O., Strizhev V.F. Numerical modeling of neutron diffusion non-stationary problems // Matematicheskoe Modelirovanie. --  2017. --  Vol. 29 (7). -- P. 44-62.

\item Avvakumov A. V., Strizhov V. F., Vabishchevich P. N., Vasilev A.O. Solution of the 3D Neutron Diffusion Benchmark by FEM // International Conference on Large-Scale Scientific Computing. -- Springer, Cham, 2017. -- P. 435-442.

\item M. Yu. Antonov, A.V. Popinako, G.A. Prokopiev, A.O. Vasilyev.  Numerical Modelling of Ion Transport in 5-HT3 Serotonin Receptor using molecular dynamics // International Conference on Numerical Analysis and Its Applications, Springer. -- 2016. -- Vol. 10187. -- P. 195-202.

\item Vasilyev A., M. Yu. Antonov, Popinako A. et al. MD simulation of dynamics and transport in 5-HT3 receptor // The Febs Journal. 2015. -- Vol. 282. -- P. 402-402.





\end{enumerate}


\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}
